% Author: Robert Konell
% Author: Blake Wellington

\documentclass{article}

\usepackage{fancyhdr}
\usepackage{amssymb}
\usepackage{amsmath}
\usepackage{color}
\usepackage{graphicx}
\usepackage{bm}
%\usepackage{tikz-er2}
%\usepackage{enumitem}
\usepackage{enumerate}
%\usepackage[LGRgreek]{mathastext}
%\usepackage{txfonts}
%\usepackage{siunitx}
%\usepackage{algorithm}
%\usepackage{algpseudocode}
\usepackage{tikz}
\usepackage{ifthen}
%\usepackage{xstring}
%\usepackage{pgfopts}
%\usepackage{tikz-qtree}
\usepackage{calc}
%\usepackage{tikz-uml}
%\usepackage{ulem}
%\usepackage{listings}
%\usepackage{pstricks,pst-uml,pstricks-add}
%\usepackage{pgffor}
%\usepackage{pgfplots}
%\usepgfplotslibrary{polar}
%\usepgflibrary{shapes.geometric}
%\usepackage{fp}
\usetikzlibrary{positioning}
\usetikzlibrary{shadows}
%\usetikzlibrary{arrows,automata,positioning,calc}
%\tikzstyle{vertex}=[draw,fill=black!15,circle,minimum size=18pt,inner sep=0pt]
%\pgfplotsset{my style/.append style={axis x line=middle, axis y line=middle, xlabel={$x$}, ylabel={$y$}, axis equal }}
%\renewcommand{\algorithmiccomment}[1]{\hskip2em$\triangleright$ #1}



%\newcommand{\sim}{\textasciitilde }
\newcommand{\conj}{\;\&\;}
\newcommand{\disj}{\; \vee \;}
\newcommand{\ntilde}{_{\widetilde{~}}}
\newcommand{\dntilde}{_{\widetilde{~}\, \widetilde{~}}}
\newcommand{\ob}{\\ {\bfseries O}}
\newcommand{\cb}{\\ {\bfseries X}}
\newcommand{\subspace}{\hspace*{4em}}


\tikzstyle{every entity} = [top color=white, bottom color=blue!30, 
                            draw=blue!50!black!100, drop shadow]
\tikzstyle{every weak entity} = [drop shadow={shadow xshift=.7ex, 
                                 shadow yshift=-.7ex}]
\tikzstyle{every attribute} = [top color=white, bottom color=yellow!20, 
                               draw=yellow, node distance=1cm, drop shadow]
\tikzstyle{every relationship} = [top color=white, bottom color=red!20, 
                                  draw=red!50!black!100, drop shadow]
\tikzstyle{every weak relationship} = [drop shadow={shadow xshift=.7ex, 
																				shadow yshift=-.7ex}]
\tikzstyle{every isa} = [top color=white, bottom color=green!20, 
                         draw=green!50!black!100, drop shadow]

\usepackage[letterpaper,
            left=3cm,right=3cm,
            top=3cm,bottom=3cm]{geometry}

\lhead{CS457}
\rhead{Project Proposal}
\chead{}                                % central header
\cfoot{}                                   % central footer (cleared)
\rfoot{Konell,Wellington \itshape \thepage}                       % right footer

\title{Project Proposal}
\author{Robert Konell, Blake Wellington}
\date{\today}

\begin{document}
\maketitle
\thispagestyle{fancy}
\pagestyle{fancy}

\section*{Summary}
The application will use data from Tri-Met's database. (Tri-Met is a 
the public transit system in Portland, Oregon). The database contains
route information for all of Tri-Met's trains and buses.

Since we are new to Haskell and have limited time to work on this project,
we have broken the project down into manageable, intermediate goals.

\section{Project Goals}
The aim of this project is to use the Haskell programming language to 
create a web-based application. It is intended as a learning exercise
with the following project goals:

* Learn functional programming with Haskell
* Learn how to use a REST API as a web service
* Learn how to use Haskell libraries to present the data
  in a meaningful way
  
\subsection{Initial Goal}
The initial goal of the project is to successfully pull a single, small
piece of information from the database, massage it in Haskell, and present
it on a web page. This may be something as basic as showing the next bus/train
to arrive at a given stop number.

\subsection{Secondary Goal}
Once the initial goal is in place, we will expand the user interface to contain
ever more complex query abilities.  For example, we might add the ability to 
select a certain route, list the stops of a route, estimate the travel time
between two stops, plan a trip (including multiple transfers), etc.

\subsection{Final Goal}
Since this is a web-based application, it would be nice to have it hosted on
a public server. The final goal is to be able to pack all the code up and 
install it on a server in the cloud (such as Amazon EC2). This will involve
installing Haskell (or just shipping the compiled version) on a server 
equipped with Apache web server.


\section*{Project Motivation} 
The authors of this application are Computer Science students at Portland
State University. We are relatively new to programming and would like to gain
experience in building applications of greater complexity than those developed
for small academic projects. As part of our requirement to use functional
programming, we will use Haskell and associated libraries to create an integrated 
piece of software with 'real world'-like behavior.

This includes using graphical libraries and/or HTML wrapper libraries for the 
front end, and calls to an exposed web API for the backend. The final user
interface will be presented on a web page using HTML (and possibly some Javascript).

\section*{Project}
A Trimet application wrapper to make use of Trimet's public web API's.
And example use case would be to submit a stop ID, and get back arrival times.

Gtk2HS is a haskell wrapper over the gtk+2.x library for creating user interfaces.

\section*{Previous experience}
Niether student has experience with user interfaces besides very mild use of the Java Swing API.  Niether student has experience interacting with web API's.  Both of these reasons are further motivation for the project.

\end{document} 